RIScatter: Unifying Backscatter Communications, Symbiotic Radio, and Reconfigurable Intelligent Surface

### 2022-10-31 main.tex
:pencil: Update scattering comparison

			The \gls{ml} decision threshold is derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,

@@

			Hence, the primary achievable rate can be approximated by\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding.}

@@

		Fig. \ref{fg:region_comparison} compares typical achieve rate points of different scattering applications.
		First, we observe both \gls{bbc} and \gls{sr} almost reach the noise-free backscatter rate when $N$ is sufficiently large.
		For \gls{bbc} with coherent energy detection, the processing loss of signal-to-energy conversion can be insignificant, thanks to the noise hardening effect at large $N$.
		For \gls{sr}, \gls{mrc} increases the equivalent backscatter \gls{snr} by $N$ times and the penalty term $\epsilon$ becomes negligible at large $N$.
		However, the backscatter rate benefit requires $N$ \gls{sic} processes per backscatter block, and the primary rate benefit under semi-coherent detection requires a very large $N$.
		When $N$ is moderate, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during primary decoding, and the \gls{sr} point will move towards \gls{ambc}.
		% Using a very large $N$ not only reduces the system throughput but also requires the operation-intensive \gls{sic} over each primary block.
		% When the primary and backscatter symbol periods are comparable, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during semi-coherent primary decoding, and the achievable rate point of \gls{sr} will move towards \gls{ambc}.
		% For a moderate $N$, the randomly scattered signals should be modelled as interference rather than quasi-static multipath components during primary decoding, and the \gls{sr} rate point will move towards \gls{ambc}.

		On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.
		% Backscatter advantage of SR using SIC is prominent for a smaller N
		% correlation by double modulation improves the detection performance
		% when $N$ is sufficiently large.
	\end{subsection}

@@

			Since \emph{Cooperation} involves full transmit cooperation of all nodes, to support independent backscatter encoding, we also propose the following methods to recover individual input distributions from the joint probability array:
			\begin{itemize}
				\item \emph{Marginalization:} Marginal probability distributions;
				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors;
				\item \emph{Randomization:} Random search guided with correlation matrix \cite{Calvo2010}.
			\end{itemize}
			% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
			% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
			% ! SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
			% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)
			Fig. \subref*{fg:region_distribution} shows the achievable rate regions for those input distribution schemes.
			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions, which suggests transmit cooperation between RIScatter nodes can be generally helpful.
			However, it requires joint encoding with arbitrarily dependent codewords, and the extra coordination burden may be unaffordable for a large $K$.
			We also notice the average performance of \emph{\gls{kkt}} input distribution design by Algorithm \ref{al:input_distribution} is extremely close to that of \emph{Exhaustion}, and the loss is indistinguishable for $K=2$.
			This verifies our claim in Remark \ref{re:input_kkt_distribution} that the average performance of \gls{kkt} solutions can be reasonably good for a moderate $K$.
			Despite \emph{Randomization} yields a similar result, the computational complexity is much higher (loops over $K+1$ linear programming problems) and the performance is backed by numerous randomly generated instances.
			In contrast, the low-complexity \emph{Marginalization} returns a comparable result and the rate loss is insignificant when $K$ is small.
			Finally, \emph{Decomposition} suffers from much lower average total backscatter rate, as the rank-\num{1} \gls{cp} approximation can be inaccurate for some channel-drop realizations.
			% Those observations demonstrate the performance and complexity advantages of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at RIScatter nodes.
			Those observations demonstrate the high performance and low complexity of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at RIScatter nodes.
		\end{subsubsection}

>>>>

			The \gls{ml} decision threshold is consequently derived as, $\forall l \in \mathcal{L} \setminus \{L\}$,

@@

			Hence, the primary achievable rate is approximately\footnote{To provide a preliminary benchmark, we consider the (correlated) scattered signal from finite-input backscatter sources as independent interference from Gaussian sources during primary decoding.}

@@

		% TODO SR analysis can achieve large rate at the cost of large N; RIScatter can achieve slightly lower rate at the same N, but also preserves primary performance for smaller N
		% TODO tradeoff between primary (RIScatter, no SIC) and backscatter (SR, SIC)
		% ! SR assume very large N for primary rate analysis. However, in such cases SIC is questionable as energy detection over received signal as BBC is already good enough and noncoherent detection can also achieve reasonable performance?
		% TODO when primary symbols are determined, optimal input distribution at high backscatter SNR is equiprobable for any detection (signal/energy)

		Fig. \ref{fg:region_comparison} compares typical achieve rate points of different scattering applications.
		First, we observe both \gls{bbc} and \gls{sr} almost achieve noise-free backscatter transmission when $N$ is sufficiently large.
		For \gls{bbc} using coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
		However, such an \gls{sr} requires $N$ \gls{sic} processes to detect one backscatter symbol (tuple), and the semi-coherent primary rate benefit only appears at a very large $N$.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than quasi-static multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		% \footnote{\gls{sr} is essentially a multiplicative \gls{noma} that cancels interference, while \gls{ambc} is essentially a multiplicative \gls{sdma} that treats interference as noise.}
		% Besides, the deterministic reflection pattern of \gls{ris} provides constructive primary signal superposition
		% \gls{ris} achieves the highest primary achievable rate using deterministic reflection pattern.
		In comparison, RIScatter performs semi-coherent backscatter detection and coherent primary detection to enable backscatter modulation and passive beamforming for arbitrary $N$, and the primary-backscatter tradeoff can be controlled by \gls{csi}- and weight-adaptive input distribution design.

		% , and different rate points can be achieved by different node input distributions.

		% coherent primary detection, and the

		% RIScatter includes

		% On the other hand, RIScatter provides a lower backscatter rate than \gls{bbc} and \gls{sr} due to semi-coherent detection, but preserves the primary rate benefit for arbitrary $N$.
		% Backscatter advantage of SR using SIC is prominent for a smaller N
		% correlation by double modulation improves the detection performance
		% when $N$ is sufficiently large.
	\end{subsection}

@@

			Since \emph{Cooperation} involves full transmit cooperation of all nodes, to support independent backscatter encoding, we also propose the following methods to recover individual input distributions from the joint probability array:
			\begin{itemize}
				\item \emph{Marginalization:} Marginal probability distributions;
				\item \emph{Decomposition:} Normalized rank-\num{1} \gls{cp} decomposition tensors;
				\item \emph{Randomization:} Random search guided with correlation matrix \cite{Calvo2010}.
			\end{itemize}
			Fig. \subref*{fg:region_distribution} shows the achievable rate regions for those input distribution schemes.
			We observe that \emph{Cooperation} provides the outer bound for all achievable rate regions, which suggests transmit cooperation between RIScatter nodes can be generally helpful.
			However, it requires joint encoding with arbitrarily dependent codewords, and the extra coordination burden may be unaffordable for a large $K$.
			We also notice the average performance of \emph{\gls{kkt}} input distribution design by Algorithm \ref{al:input_distribution} is extremely close to that of \emph{Exhaustion}, and the loss is indistinguishable for $K=2$.
			This verifies our claim in Remark \ref{re:input_kkt_distribution} that the average performance of \gls{kkt} solutions can be reasonably good for a moderate $K$.
			Despite \emph{Randomization} yields a similar result, the computational complexity is much higher (loops over $K+1$ linear programming problems) and the performance is backed by numerous randomly generated instances.
			In contrast, the low-complexity \emph{Marginalization} returns a comparable result and the rate loss is insignificant when $K$ is small.
			Finally, \emph{Decomposition} suffers from much lower average total backscatter rate, as the rank-\num{1} \gls{cp} approximation can be inaccurate for some channel-drop realizations.
			% Those observations demonstrate the performance and complexity advantages of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at RIScatter nodes.
			Those observations demonstrate the high performance and low complexity of the proposed \gls{kkt} input distribution design, and reveal the potential of joint encoding at RIScatter nodes.
		\end{subsubsection}
